Kids SUMs Summary

### 2020-02-13 home_char_act_summary.Rmd
summary stats update

## Select specific var to assess individually/group by area
table(table_list$winter_id, table_list$area, table_list$home_type, useNA = "ifany")
```

@@

>>>>

## Select specific var to assess individually/group by area
table(table_list$winter_id, table_list$area, table_list$home_type, useNA = "ifany")

table(home_char_summary$stove_age)
```

@@

home_char_filtered %>% 
  count(stove_age)

### 2020-02-13 sums_summary.Rmd
summary stats update

@@

>>>>

# Closer look at negative temperatures
```{r}
total_homes <- sums_clean %>% 
  filter(winter_id == 1) %>% 
  count(home)

home_neg <- sums_clean %>% 
  filter(winter_id == 1) %>% 
  mutate(neg_temp = if_else(temp_c_sums < 0, 1, 0)) %>% 
  filter(neg_temp == 1) %>% 
  count(home) %>% 
  mutate(home_neg_temp = 1) %>% 
  select(home, home_neg_temp)

total_instruments <- sums_clean %>% 
  filter(winter_id == 1) %>% 
  count(ibid)

instrument_neg <- sums_clean %>% 
  filter(winter_id == 1) %>% 
  mutate(neg_temp = if_else(temp_c_sums < 0, 1, 0)) %>% 
  filter(neg_temp == 1) %>% 
  count(ibid) %>% 
  mutate(instrument_neg_temp = 1) %>% 
  select(ibid, instrument_neg_temp)

sums_neg_check <- sums_clean %>% 
  filter(winter_id == 1) %>% 
  left_join(home_neg, by = "home") %>% 
  left_join(instrument_neg, by = "ibid") %>% 
  mutate(home_neg_temp = if_else(is.na(home_neg_temp), 0, home_neg_temp),
         instrument_neg_temp = if_else(is.na(instrument_neg_temp), 0, instrument_neg_temp)) %>% 
  # group by both home_neg_temp and instrument_neg_temp to check summaries
  group_by(home_neg_temp) %>% 
  summarize("mean" = mean(temp_c_sums, na.rm = TRUE),
            "n" = n(),
            "min" = min(temp_c_sums, na.rm = TRUE),
            "median" = median(temp_c_sums, na.rm = TRUE),
            "max" = max(temp_c_sums, na.rm = TRUE))
sums_neg_check
```

The summaries above indicate that homes that had negative temperatures have similar
summary stats to those that did not have negative temps. The same is true for
the instruments used to measure temperature: instruments that had negative readings
have similar summary stats to those without negative readings. This gives some
reassurance that there are not any obvious trends associated with homes or
instruments that recorded negative temperatures during sampling.

@@

# Define events by rate of change in temperature
```{r}
sums_temp_change <- sums_clean %>% 
  filter(winter_id == 1) %>% 
  group_by(area, home) %>% 
  mutate(time_diff = lead(datetime_sums) - datetime_sums) %>% 
  mutate(lead_temp = if_else(time_diff < 20, lead(temp_c_sums, 4), lead(temp_c_sums)),
         lead_temp = if_else(time_diff > 25, temp_c_sums, lead_temp),
         temp_diff = lead_temp - temp_c_sums,
         temp_diff_av = abs(lead_temp - temp_c_sums),
         temp_diff_check = if_else(temp_diff >= 5, 1, 0),
         heat_event = if_else(temp_diff_check == 1 & lag(temp_diff_check) == 1, 0,
                              temp_diff_check)) %>% 
  ungroup() %>% 
  arrange(area, home, datetime_sums)

summary_by_area <- sums_temp_change %>% 
  group_by(area, home, date_sums) %>% 
  summarize("events" = sum(heat_event, na.rm = TRUE)) %>% 
  group_by(area) %>% 
  summarize("Mean events" = mean(events),
            "SD events" = sd(events),
            "Min events" = min(events),
            "Median events" = median(events),
            "Max events" = max(events))
summary_by_area

temp_diff_by_area <- sums_temp_change %>% 
  mutate(time_diff = as.numeric(time_diff)) %>% 
  filter(time_diff >= 5 & time_diff < 30) %>% 
  group_by(area) %>% 
  summarize("mean temp diff" = mean(temp_diff_av, na.rm = TRUE),
            "mean time diff" = mean(time_diff, na.rm = TRUE))
temp_diff_by_area
```
